Sexual selection improves population fitness: a meta-analysis

### 2018-06-20 meta_analysis_sexual_selection_pop_fitness.Rmd
20/6 Update

---
title: 'Sexual selection improves fitness: a meta-analysis'
author: "Justin G. Cally^1^, Luke Holman^1^, Devi Stuart-Fox^1^ <br></br> <br></br> ^1^The University of Melbourne"
subtitle: Supplementary Material
output:
  html_document:
    toc: true # table of content true
    toc_float: true # make 
    depth: 3  # upto three depths of headings (specified by #, ## and ###)
    number_sections: false  ## if you want number sections at each table header
    theme: yeti # lovely fonts and colours
    code_folding: hide # awesome buttons to show/hide the code
  pdf_document: default
---

```{r, warning=FALSE, message=FALSE, results='hide'}
library(pander)
library(tidyr)
library(compute.es)
library(metafor)
library(plyr)
library(dplyr)
library(lme4)
library(car)
library(forestplot)
library(ggplot2)
library(ggthemes)
library(kableExtra)
library(ggrepel)
library(reshape2)
library(RColorBrewer)
library(ggridges)
library(rstan) #Note that installation requires some effort: dependency for brms
library(brms) 
library(backports) #seems to be a dependency
library(bayesplot)
#devtools::install_github("mvuorre/brmstools")
library(brmstools) 
source("Vdodge_function.R") # nice function for ggplot
source("Tidy_functions_for_brms.R") #Tidy functions for making model tables for brms
```

@@

Our aim was to investigate the effects of sexual selection on population fitness by conducting a meta-analysis on studies that measured fitness related outcomes after experimentally evolving a population under varying levels of opportunity for sexual selection. Here we describe the process of the literature search, data extraction, effect size calculation, formulation of multilevel models and assessing publication bias.

@@

1. We searched ISI Web of Science and Scopus on 9th June 2017. The two search engines produded a somewhat different set of papers (**PRISMA Figure**).

@@

In addition to studies found from the literature search we also included three relevant studies that we found, which were not picked up in the subsequent formal searches (Partridge 1980; Price et al. 2010; Savic Veselinovic et al. 2013; **PRISMA Figure**).

@@

After removing duplicates papers recovered from both ISI and Scopus, we read the titles and abstracts of the remaining 1015 papers, and removed papers that were not relevant (typically because they were not an empirical study using experimental evolution). This left 130 papers, for which we read the full text and applied the following selection criteria:

  + **(1: Study Design)** The study was an experimental evolution study lasting >1 generation
  + **(1: Population)** a) The study was conducted using an animal species that was b) diecious
  + **(1: Intervention and Control)** The study experimentally manipulated the strength of sexual selection (e.g. via enforced monogamy or an altered sex ratio)
  + **(1: Outcomes)** The study measured a trait that we judged to be a potential correlate of population fitness.

@@

 <br/><br/>
```{r, warning=FALSE}
outcome.descriptions <- read.csv('data/outcome.descriptions.csv', 
                                 fileEncoding="UTF-8")
kable(outcome.descriptions, "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "500px")
```
  <br/><br/> 
<input type=button class=hideshow></input>
```{r, warning=FALSE}
outcome.references <- read.csv('data/references.tableS1.csv', 
                                 fileEncoding="UTF-8")
kable(outcome.references, "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "250px")
```
  <br/><br/>

**Table S2:** An eligibility criteria was based on four features a study needed to include (discussed above), to be eligable for inclusion in the meta-analysis the study needed to satisfy all criteria. Here we applied a step-wise process to the studies that had their full-text read and excluded them when they first failed to meet the criteria. Additional notes documenting reasons behind exclusion were also taken.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r}
Eligibility.criteria <- read.csv('data/Eligibility Workbook(22.02).csv', 
                                 fileEncoding="UTF-8")
kable(Eligibility.criteria, "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "500px")
```

@@

3. If means were not reported then we extracted a summary statistic or proportion value, which we could later convert to Hedges g' using the _compute.es_ package. Summary statistics included _F_, _z_, _t_ and _chi^2^_. These conversions still required providing sample sizes for each treatment so these needed to be extractable from the study. Some summary statistics were obtained from generalized linear model summary tabels, others from straight forward ANOVAs and then some from more complex analysis such as proportional hazards statistical tests.

@@

kable(prelim.data, "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "500px")
```
<br></br>

@@

**Positive Fitness**: Whether the measurment used in the study is beneficial for fitness (1) or not (0). Note that g has already been multiplied by this column.

@@

### Table of sample sizes

The number of effect sizes, publications, blind experiments, effect sizes in stressed conditions, male, female and both measures and different species used, with the number of effect sizes per taxon also reported.

**Table S4:** Table of effect sizes included in our meta-analysis. See the text following the data table for an explanation of each column.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r message=FALSE, warning=FALSE}
n.blind.ones <- (sum(prelim.data$Blind == "Blind"))
prelim.data %>% 
  summarise(
    Effect_sizes_.Totalq = n(), 
    Publications = prelim.data$Study.ID %>% unique() %>% length(),
    Blind_experiments = n.blind.ones,
    Effect_sizes_.Stressedq = (sum(prelim.data$Environment == "Stressed")),
    Effect_sizes_.Unstressedq = (sum(prelim.data$Environment == "Unstressed")),         
    Effect_sizes_.Maleq = (sum(prelim.data$Sex == "M")),
    Effect_sizes_.Femaleq = (sum(prelim.data$Sex == "F")),
    Effect_sizes_.Both_sexesq = (sum(prelim.data$Sex == "B")),
    Different_species =  prelim.data$Species %>% unique() %>% length(),
    Effect_sizes_.Beetleq = sum(Taxon == "Beetle"),
    Effect_sizes_.Flyq = sum(Taxon == "Fly"),
    Effect_sizes_.Mouseq = sum(Taxon == "Mouse"),
    Effect_sizes_.Nematodeq = sum(Taxon == "Nematode"),
    Effect_sizes_.Miteq = sum(Taxon == "Mite"),
    Effect_sizes_.Cricketq = sum(Taxon == "Cricket"),
    Effect_sizes_.Guppyq = sum(Taxon == "Guppy")) %>% melt() %>%
  mutate(variable = gsub("_", " ", variable),
         variable = gsub("[.]", "(", variable),
         variable = gsub("q", ")", variable)) %>% 
  rename_("n" = "value", " " = "variable") %>% 
  pander(split.cell = 40, split.table = Inf)
```
 <br/><br/> 
**Table S5:** Table of fitness outcomes included in our meta-analysis by sex.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r}
Outcome_and_sex <- as.data.frame.matrix(table(prelim.data$Outcome, prelim.data$Sex))
colnames(Outcome_and_sex) <- cbind("Both", "Female", "Male")

@@

### Forest plot

Here we show the raw effect sizes for each fitness component measured.

@@

  # scale_color_discrete(breaks=c("Ambiguous","Indirect","Direct"))+
  theme_bw()+

@@

p.meta

@@

# svg("figures/Big_forest_plot.svg", width=12, height=18)
# p.meta
# dev.off()
# 
# pdf("figures/Big_forest_plot.pdf", width=12, height=18)
# p.meta
# dev.off()
```
<br></br>
**Figure S1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to measured fitness components and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together). Rows with multiple data points denote studies that provided multiple effect sizes. Positive values indicate fitness benefits of sexual selection.

___________

###Meta-analysis of individual outcomes

We can run individual standard random effects models for each outcome. From the intercept only model we can obtain a mean (beta) and confidence intervals. Following that we can obtain estimates for _I^2^_, the % of residual heterogeneity for each given outcome.

**Table S6** Summary of individual model results, including _I^2^_, for all outcomes with n>3. 
<input type=button class=hideshow></input>
```{r, warning = FALSE}
outcome.list <- as.list(c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))
names(outcome.list) <- c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
outcome.models <-  llply(outcome.list, function(x) rma.mv(g, var.g, 
                          mods = ~ 1, 
                          method = "REML",
                          random = ~ 1 + Study.ID,
                          subset = (Outcome_f == x),
                          data = prelim.data))

df.list <- as.data.frame(do.call("rbind", outcome.models)) # data frame of model results

simple.frame <- subset(df.list, select=c("b", "zval", "ci.lb", "ci.ub", "k", "pval"))

#There is no simple way to get I2 for multilevel models in metafor, so we can obtain them manually for each outcome

#Body Size 
restricted.dataBS <- prelim.data %>% filter(prelim.data$Outcome == "Body Size")

#Run estimate of heterogeneity
WBS = diag(1/restricted.dataBS$var.g)
XBS = model.matrix(outcome.models[["Body Size"]])
PBS = WBS - WBS %*% XBS %*% solve(t(XBS) %*% WBS %*% XBS) %*% t(XBS) %*% WBS
BodySizeI2 <- 100 * sum(outcome.models[["Body Size"]]$sigma2) / (sum(outcome.models[["Body Size"]]$sigma2) + (outcome.models[["Body Size"]]$k-outcome.models[["Body Size"]]$p)/sum(diag(PBS)))

#Development Rate 
restricted.dataDR <- prelim.data %>% filter(prelim.data$Outcome == "Development Rate")

#Run estimate of heterogeneity
W = diag(1/restricted.dataDR$var.g)
X = model.matrix(outcome.models[["Development Rate"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
DevelopmentRateI2 <- 100 * sum(outcome.models[["Development Rate"]]$sigma2) / (sum(outcome.models[["Development Rate"]]$sigma2) + (outcome.models[["Development Rate"]]$k-outcome.models[["Development Rate"]]$p)/sum(diag(P)))

#Early Fecundity 
restricted.dataEF <- prelim.data %>% filter(prelim.data$Outcome == "Early Fecundity")

#Run estimate of heterogeneity
W = diag(1/restricted.dataEF$var.g)
X = model.matrix(outcome.models[["Early Fecundity"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
EarlyFecundityI2 <- 100 * sum(outcome.models[["Early Fecundity"]]$sigma2) / (sum(outcome.models[["Early Fecundity"]]$sigma2) + (outcome.models[["Early Fecundity"]]$k-outcome.models[["Early Fecundity"]]$p)/sum(diag(P)))

#Immunity
restricted.dataI <- prelim.data %>% filter(prelim.data$Outcome == "Immunity")

#Run estimate of heterogeneity
W = diag(1/restricted.dataI$var.g)
X = model.matrix(outcome.models[["Immunity"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
ImmunityI2 <- 100 * sum(outcome.models[["Immunity"]]$sigma2) / (sum(outcome.models[["Immunity"]]$sigma2) + (outcome.models[["Immunity"]]$k-outcome.models[["Immunity"]]$p)/sum(diag(P)))

#Mating Duration
restricted.dataMD <- prelim.data %>% filter(prelim.data$Outcome == "Mating Duration")

#Run estimate of heterogeneity
W = diag(1/restricted.dataMD$var.g)
X = model.matrix(outcome.models[["Mating Duration"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
MatingDurationI2 <- 100 * sum(outcome.models[["Mating Duration"]]$sigma2) / (sum(outcome.models[["Mating Duration"]]$sigma2) + (outcome.models[["Mating Duration"]]$k-outcome.models[["Mating Duration"]]$p)/sum(diag(P)))

#Mutant Frequency
restricted.dataMF <- prelim.data %>% filter(prelim.data$Outcome == "Mutant Frequency")

#Run estimate of heterogeneity
W = diag(1/restricted.dataMF$var.g)
X = model.matrix(outcome.models[["Mutant Frequency"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
MutantFrequencyI2 <- 100 * sum(outcome.models[["Mutant Frequency"]]$sigma2) / (sum(outcome.models[["Mutant Frequency"]]$sigma2) + (outcome.models[["Mutant Frequency"]]$k-outcome.models[["Mutant Frequency"]]$p)/sum(diag(P)))

#Fitness Senescence
restricted.dataFS <- prelim.data %>% filter(prelim.data$Outcome == "Fitness Senescence")

#Run estimate of heterogeneity
W = diag(1/restricted.dataFS$var.g)
X = model.matrix(outcome.models[["Fitness Senescence"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
FitnessSenescenceI2 <- 100 * sum(outcome.models[["Fitness Senescence"]]$sigma2) / (sum(outcome.models[["Fitness Senescence"]]$sigma2) + (outcome.models[["Fitness Senescence"]]$k-outcome.models[["Fitness Senescence"]]$p)/sum(diag(P)))

#Lifespan
restricted.dataL <- prelim.data %>% filter(prelim.data$Outcome == "Lifespan")

#Run estimate of heterogeneity
W = diag(1/restricted.dataL$var.g)
X = model.matrix(outcome.models[["Lifespan"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
LifespanI2 <- 100 * sum(outcome.models[["Lifespan"]]$sigma2) / (sum(outcome.models[["Lifespan"]]$sigma2) + (outcome.models[["Lifespan"]]$k-outcome.models[["Lifespan"]]$p)/sum(diag(P)))

#Male Attractiveness
restricted.dataMA <- prelim.data %>% filter(prelim.data$Outcome == "Male Attractiveness")

#Run estimate of heterogeneity
W = diag(1/restricted.dataMA$var.g)
X = model.matrix(outcome.models[["Male Attractiveness"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
MaleAttractivenessI2 <- 100 * sum(outcome.models[["Male Attractiveness"]]$sigma2) / (sum(outcome.models[["Male Attractiveness"]]$sigma2) + (outcome.models[["Male Attractiveness"]]$k-outcome.models[["Male Attractiveness"]]$p)/sum(diag(P)))

#Mating Frequency
restricted.dataMF <- prelim.data %>% filter(prelim.data$Outcome == "Mating Frequency")

#Run estimate of heterogeneity
W = diag(1/restricted.dataMF$var.g)
X = model.matrix(outcome.models[["Mating Frequency"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
MatingFrequencyI2 <- 100 * sum(outcome.models[["Mating Frequency"]]$sigma2) / (sum(outcome.models[["Mating Frequency"]]$sigma2) + (outcome.models[["Mating Frequency"]]$k-outcome.models[["Mating Frequency"]]$p)/sum(diag(P)))

#Mating Latency
restricted.dataML <- prelim.data %>% filter(prelim.data$Outcome == "Mating Latency")

#Run estimate of heterogeneity
W = diag(1/restricted.dataML$var.g)
X = model.matrix(outcome.models[["Mating Latency"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
MatingLatencyI2 <- 100 * sum(outcome.models[["Mating Latency"]]$sigma2) / (sum(outcome.models[["Mating Latency"]]$sigma2) + (outcome.models[["Mating Latency"]]$k-outcome.models[["Mating Latency"]]$p)/sum(diag(P)))

#Mating Success
restricted.dataMS <- prelim.data %>% filter(prelim.data$Outcome == "Mating Success")

#Run estimate of heterogeneity
W = diag(1/restricted.dataMS$var.g)
X = model.matrix(outcome.models[["Mating Success"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
MatingSuccessI2 <- 100 * sum(outcome.models[["Mating Success"]]$sigma2) / (sum(outcome.models[["Mating Success"]]$sigma2) + (outcome.models[["Mating Success"]]$k-outcome.models[["Mating Success"]]$p)/sum(diag(P)))

#Ejaculate Quality and Production
restricted.dataEQ <- prelim.data %>% filter(prelim.data$Outcome == "Ejaculate Quality and Production")

#Run estimate of heterogeneity
W = diag(1/restricted.dataEQ$var.g)
X = model.matrix(outcome.models[["Ejaculate Quality and Production"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
EjaculateQualityI2 <- 100 * sum(outcome.models[["Ejaculate Quality and Production"]]$sigma2) / (sum(outcome.models[["Ejaculate Quality and Production"]]$sigma2) + (outcome.models[["Ejaculate Quality and Production"]]$k-outcome.models[["Ejaculate Quality and Production"]]$p)/sum(diag(P)))

#Extinction Rate
restricted.dataER <- prelim.data %>% filter(prelim.data$Outcome == "Extinction Rate")

#Run estimate of heterogeneity
W = diag(1/restricted.dataER$var.g)
X = model.matrix(outcome.models[["Extinction Rate"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
ExtinctionRateI2 <- 100 * sum(outcome.models[["Extinction Rate"]]$sigma2) / (sum(outcome.models[["Extinction Rate"]]$sigma2) + (outcome.models[["Extinction Rate"]]$k-outcome.models[["Extinction Rate"]]$p)/sum(diag(P)))

#Offspring Viability
restricted.dataOV <- prelim.data %>% filter(prelim.data$Outcome == "Offspring Viability")

#Run estimate of heterogeneity
W = diag(1/restricted.dataOV$var.g)
X = model.matrix(outcome.models[["Offspring Viability"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
OffspringViabilityI2 <- 100 * sum(outcome.models[["Offspring Viability"]]$sigma2) / (sum(outcome.models[["Offspring Viability"]]$sigma2) + (outcome.models[["Offspring Viability"]]$k-outcome.models[["Offspring Viability"]]$p)/sum(diag(P)))

#Reproductive Success
restricted.dataRS <- prelim.data %>% filter(prelim.data$Outcome == "Reproductive Success")

#Run estimate of heterogeneity
W = diag(1/restricted.dataRS$var.g)
X = model.matrix(outcome.models[["Reproductive Success"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
ReproductiveSuccessI2 <- 100 * sum(outcome.models[["Reproductive Success"]]$sigma2) / (sum(outcome.models[["Reproductive Success"]]$sigma2) + (outcome.models[["Reproductive Success"]]$k-outcome.models[["Reproductive Success"]]$p)/sum(diag(P)))

simple.frame$I2 <- c(NA, BodySizeI2, DevelopmentRateI2, EarlyFecundityI2, ImmunityI2, MatingDurationI2, NA, MutantFrequencyI2, FitnessSenescenceI2, LifespanI2, MaleAttractivenessI2, MatingFrequencyI2, MatingLatencyI2, MatingSuccessI2, NA, EjaculateQualityI2, ExtinctionRateI2, OffspringViabilityI2, ReproductiveSuccessI2)

outcome.frame <- format(simple.frame, digits = 2)
outcome.frame <- add_rownames(outcome.frame, "Outcome")
outcome.frame$b <- as.numeric(outcome.frame$b)
outcome.frame$k <- as.numeric(outcome.frame$k)
outcome.frame$ci.lb <- as.numeric(outcome.frame$ci.lb)
outcome.frame$ci.ub <- as.numeric(outcome.frame$ci.ub)
outcome.frame$I2 <- as.numeric(outcome.frame$I2)
outcome.frame$Class <- c("Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Ambiguous", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Indirect", "Direct", "Direct", "Direct")

#Only present subset model results for outcomes with 4 or more effect sizes

outcome.frame %>% filter(Outcome != "Behavioural Plasticity" & Outcome != "Pesticide Resistance" & Outcome != "Strength") %>% pander(split.cell = 40, split.table = Inf)
```

@@

## Multilevel Meta-Analysis

@@

We collected data from fitness components that were deemed ambiguous as well as unambiguous. The ambiguous outcomes are likely to add in heterogeneity to the models and not help us in answering questions of fitness effects of sexual selection. A model utilising our complete dataset with many moderator variables would thus be:

@@

First we want to run the model using a restricted dataset where we remove effect sizes with Ambiguous outcomes (directionless or variable in their relation to fitness) or environments that were not stated whether they were stressed or unstressed (confusing and confounding). In this model we use Sex, Environment, Taxon and the interaction between sex and environment.

>>>>

---
title: 'Sexual selection improves population fitness: a meta-analysis'
author: "Justin G. Cally^1^, Luke Holman^1^, Devi Stuart-Fox^1^ <br></br> <br></br> ^1^The University of Melbourne"
subtitle: Supplementary Material
bibliography: bibliography_meta_analysis.bib
output:
  html_document:
    toc: true # table of content true
    toc_float: true # make 
    depth: 3  # upto three depths of headings (specified by #, ## and ###)
    number_sections: false  ## if you want number sections at each table header
    theme: yeti # lovely fonts and colours
    code_folding: hide # awesome buttons to show/hide the code
  pdf_document: default
---

```{r, warning=FALSE, message=FALSE, results='hide'}
library(pander)
library(tidyr)
library(compute.es)
library(metafor)
library(plyr)
library(dplyr)
library(lme4)
library(car)
library(forestplot)
library(ggplot2)
library(ggthemes)
library(kableExtra)
library(ggrepel)
library(reshape2)
library(RColorBrewer)
library(ggridges)
library(rstan) #Note that installation requires some effort: dependency for brms
library(brms) 
library(backports) #seems to be a dependency
library(bayesplot)
#devtools::install_github("mvuorre/brmstools")
library(brmstools)
library(metaAidR)
source("I2_function.R") #Adapted function for obtaining I2 with CIs
source("Vdodge_function.R") # nice function for ggplot
source("Tidy_functions_for_brms.R") #Tidy functions for making model tables for brms
```

@@

Our aim was to investigate the effects of sexual selection on population fitness by conducting a meta-analysis on studies that measured fitness related outcomes after experimentally evolving a population under varying levels of opportunity for sexual selection. Here we describe the process of the literature search, data extraction, effect size calculation, formulation of multilevel models and assessing publication bias. We used the PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses) as a guide during this meta-analysis.

@@

1. We searched ISI Web of Science and Scopus on 9th June 2017. The two search engines produded a somewhat different set of papers (**see PRISMA Figure in manuscript**).

@@

In addition to studies found from the literature search we also included three relevant studies that we found, which were not picked up in the subsequent formal searches [@Partridge_1980; @Price_2010; @Savic_2013] **see PRISMA Figure in manuscript**.

@@

After removing duplicates papers recovered from both _Web of Science_ and _Scopus_, we read the titles and abstracts of the remaining 1015 papers, and removed papers that were not relevant (typically because they were not an empirical study using experimental evolution). This left 130 papers, for which we read the full text and applied the following selection criteria:

  + **(1: Study Design)** The study was an experimental evolution study lasting >1 generation
  + **(2: Population)** a) The study was conducted using an animal species that was b) dioecious
  + **(3: Intervention and Control)** The study experimentally manipulated the strength of sexual selection for at least one generation (e.g. via enforced monogamy or an altered sex ratio)
  + **(4: Outcomes)** The study measured a trait that we judged to be a potential correlate of population fitness.

@@

 <br/><br/>
```{r, warning=FALSE}
outcome.descriptions <- read.csv('data/outcome.descriptions.csv', 
                                 fileEncoding="UTF-8")
kable(outcome.descriptions, "html") %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "500px")
```
  <br/><br/> 
<input type=button class=hideshow></input>
```{r, warning=FALSE}
outcome.references <- read.csv('data/references.tableS1.csv', 
                                 fileEncoding="UTF-8")
kable(outcome.references, "html") %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "250px")
```
  <br/><br/>

**Table S2:** An eligibility criteria was based on four features a study needed to include (discussed above), to be eligable for inclusion in the meta-analysis the study needed to satisfy all criteria. Here we applied a step-wise process to the studies that had their full-text read and excluded them when they first failed to meet the criteria. Additional notes documenting reasons behind exclusion were also taken.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r}
Eligibility.criteria <- read.csv('data/Eligibility Workbook(22.02).csv', 
                                 fileEncoding="UTF-8")
kable(Eligibility.criteria, "html") %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "500px")
```

@@

3. If means were not reported then we extracted a summary statistic or proportion value, which we could later convert to Hedges g' using the _compute.es_ package [@compute_es]. Summary statistics included _F_, _z_, _t_ and _chi^2^_. These conversions still required providing sample sizes for each treatment so these needed to be extractable from the study. Some summary statistics were obtained from generalized linear model summary tabels, others from straight forward ANOVAs and then some from more complex analysis such as proportional hazards statistical tests.

@@

kable(prelim.data, "html") %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "500px")
```
<br></br>

@@

**Positive Fitness**: Whether the measurment used in the study is beneficial for fitness (1) or not (0). Note that g has already been multiplied by this column. We inverted all of the effect sizes pertaining to fitness outcomes that are expected to be negatively related to fitness by multiplying the effect size by -1.

@@

### Tables of Sample Sizes

Here we present the number of effect sizes, publications, blind experiments, effect sizes in stresful conditions, male, female and both measures and different species used.

**Table S4:** Table of effect sizes included in our meta-analysis. See the text following the data table for an explanation of each column.
 <br/><br/> 
```{r message=FALSE, warning=FALSE}
n.blind.ones <- (sum(prelim.data$Blind == "Blind"))
prelim.data %>% 
  summarise(
    Effect_sizes_.Totalq = n(), 
    Publications = prelim.data$Study.ID %>% unique() %>% length(),
    Blind_experiments = n.blind.ones,
    Effect_sizes_.Enforced_monogamyq = (sum(prelim.data$Enforced.Monogamy == "YES")),
    Effect_sizes_.Ambiguousq = (sum(prelim.data$Outcome.Class == "Ambiguous")),
    Effect_sizes_.Indirectq = (sum(prelim.data$Outcome.Class == "Indirect")),
    Effect_sizes_.Directq = (sum(prelim.data$Outcome.Class == "Direct")),
    Effect_sizes_.Stressedq = (sum(prelim.data$Environment == "Stressed")),
    Effect_sizes_.Unstressedq = (sum(prelim.data$Environment == "Unstressed")),         
    Effect_sizes_.Maleq = (sum(prelim.data$Sex == "M")),
    Effect_sizes_.Femaleq = (sum(prelim.data$Sex == "F")),
    Effect_sizes_.Both_sexesq = (sum(prelim.data$Sex == "B")),
    Different_species =  prelim.data$Species %>% unique() %>% length(),
    Effect_sizes_.Beetleq = sum(Taxon == "Beetle"),
    Effect_sizes_.Flyq = sum(Taxon == "Fly"),
    Effect_sizes_.Mouseq = sum(Taxon == "Mouse"),
    Effect_sizes_.Nematodeq = sum(Taxon == "Nematode"),
    Effect_sizes_.Miteq = sum(Taxon == "Mite"),
    Effect_sizes_.Cricketq = sum(Taxon == "Cricket"),
    Effect_sizes_.Guppyq = sum(Taxon == "Guppy")) %>% melt() %>%
  mutate(variable = gsub("_", " ", variable),
         variable = gsub("[.]", "(", variable),
         variable = gsub("q", ")", variable)) %>% 
  rename_("n" = "value", " " = "variable") %>% 
  pander(split.cell = 40, split.table = Inf)
```
 <br/><br/> 
**Table S5:** Table of fitness outcomes included in our meta-analysis by sex.
 <br/><br/> 
```{r}
Outcome_and_sex <- as.data.frame.matrix(table(prelim.data$Outcome, prelim.data$Sex))
colnames(Outcome_and_sex) <- cbind("Both", "Female", "Male")

@@

### Forest Plot

@@

  #Add theme specifying text size, margins, lines etc.
  theme_bw()+

@@

@@

# svg("figures/Big_forest_plot.svg", width=12, height=18)
# p.meta
# dev.off()
# 
# pdf("figures/Big_forest_plot.pdf", width=12, height=18)
# p.meta
# dev.off()

p.meta
```
<br></br>
**Figure S1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to measured fitness components and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together). Rows with multiple data points denote studies that provided multiple effect sizes. Positive values indicate fitness benefits of sexual selection.

@@

## Meta-Analysis

###Overall effect of sexual selection on fitness

We can obtain an overall weghted grand mean and confidence intervals with a simple intercept only for both Bayesian and REML models. Notably, in both models the estimates are approximately the same, with Bayesian estimates being marginally wider.

```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE, eval=FALSE}
grand.mean.bayes <- brm(g | se(SE)  ~ 1 #Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
                + (1|Study.ID)
                + (1|Outcome), 
                family = "gaussian", 
                seed = 1,
                cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
                control = list(adapt_delta = 0.9999, max_treedepth = 15),
                data = prelim.data %>% mutate(SE = sqrt(var.g)))

```

```{r}
grand.mean.bayes <- readRDS("data/grand.mean.bayes.rds")

#Run REML model 
forest.model <- rma.mv(g, var.g,
                       mods = ~ 1,
                       random = list(~ 1 | Study.ID,
                                      ~ 1 | Outcome),
                       method = "REML",
                       data = prelim.data)

#Manually imput bayesian results
mean = c(forest.model$b, 0.22)
LCI = c(forest.model$ci.lb, 0.01)
UCI = c(forest.model$ci.ub, 0.43)
grand.means.df <- data.frame(rbind(mean, LCI, UCI))
colnames(grand.means.df) = c("REML", "Bayesian")
grand.means.df %>% pander(digits = 2)
```

###Effect of Sexual Selection for different fitness components

Instead of running individual models for each fitness component we can run a model with the fitness components as predictors. In this case we maintain all of our fitness components and include study.id as a group level effect (to account for within study correlations in effect size). Using the ``brms`` package we can run a Bayesian model and generate fitted values for each fitness component.
```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE, eval=FALSE}
model.fitness.components.bayes <- brm(g | se(SE)  ~ Outcome #Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
                + (1|Study.ID), 
                family = "gaussian", 
                seed = 1,
                cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
                control = list(adapt_delta = 0.999, max_treedepth = 15),
                data = prelim.data %>% mutate(SE = sqrt(var.g)))

make_text_summary(model.fitness.components.bayes) %>% add_significance_stars() %>% tibble::rownames_to_column("Model Parameter") %>% pander(split.cell = 40, split.table = Inf)
```

**Table S6** Summary of model predictions for 20 fitness components. In the manuscript these values are presented as a text overlay on Figure 1 (Forest Plot).

```{r, warning = FALSE}
components.brms <- readRDS(file = "data/components.brms.rds") #Avoid re-running model above

#Expand grid for environment and sex
brms.newdata <- as.data.frame(expand.grid(Outcome = unique(prelim.data$Outcome)))

#Get average SE: useful if using predict, but not fitted
av.se.g <- prelim.data %>% group_by(Outcome) %>% summarise(mean = mean(sqrt(var.g)))
brms.newdata$SE <- av.se.g$mean

#Add predictions/fitted values
brms.predict <- fitted(components.brms, newdata = brms.newdata, re_formula = NA)
brms.predict <- as.data.frame(brms.predict)
brms.predictions <- data.frame(brms.newdata$Outcome, brms.predict$Estimate, brms.predict$Est.Error, brms.predict$Q2.5, brms.predict$Q97.5)

#Name columns
colnames(brms.predictions) <- c("Fitness Component", "Estimate", "Error", "LCI", "UCI")

outcome.list.factor <-  c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')

brms.predictions <- brms.predictions[match(outcome.list.factor, brms.predictions$`Fitness Component`),]
rownames(brms.predictions) <- NULL
sample.sizes.outcomes <- as.data.frame(table(prelim.data$Outcome))
colnames(sample.sizes.outcomes) <- c("Fitness Component", "n")
fitness.component.predictions <- left_join(brms.predictions, sample.sizes.outcomes, by = "Fitness Component")
fitness.component.predictions %>% add_significance_stars2() %>% pander(split.cell = 40, split.table = Inf, digits = 2)
```

@@

We collected data from fitness components that were deemed ambiguous as well as unambiguous. The ambiguous outcomes are likely to add in heterogeneity to the models and may not help us in answering questions of the fitness effects of sexual selection. A REML model utilising our complete dataset with many moderator variables would thus be:

@@

First we want to run the model using a restricted dataset where we remove effect sizes with Ambiguous outcomes (directionless or variable in their relation to fitness) or environments that were not stated whether they were stressed or unstressed (confusing and confounding). Notably, with the ambiguous measures included we already see a positive effect of sexual selection and thus removing these fitness components is not an attempt to obtain a significant answer, rather it restricts the data to traits that are less contentious and thus we believe this approach is conservative. In this model we use Sex, Environment, Taxon and the interaction between sex and environment.
